Reconstructing Propositional Proofs in Type Theory

### 2017-10-24 paper/sections/introduction.tex
[ paper ] fixed some text in intro.

\section{Introduction (ESCRIBIENDO)}
\label{sec:introduction}

Reconstructing and verifying proofs delivered by automatic theorem provers
(henceforth ATP) are non-trivial tasks.
In the last decades, \ATPs is fast becoming a key instrument in 
different disciplines (\eg verifying cryptographic protocols for information security) and researchers have shown an increased interest to prove the validity of the deduction algorithms.
One reason to say that is the bugs found in many ATPs~\cite{Keller2013,Bohme2011,Fleury2014}.
For that reason, in order to give confidence to the user of these systems,
many ATPs has started to include in their outputs, the proofs of the
conclusion. However, existing research recognizes that in many cases these proofs encode non-trivial reasoning
hard to reconstruct them and therefore to verify them.

Hence proof-reconstructing becomes a reverse engineering task
in which the source, the proof, and its quality play an important role.
To begin with the proof-reconstruction, it is necessary to have
the proof of the \ATP in a consistent format, that is, a full script 
describing step-by-step with exhaustive details and without ambiguities, the 
derivation to get the actual proof.  
For classical propositional logic (henceforth \CPL), from a list of at least forty\footnote{\ATPs 
available from the web
service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
provers were able to deliver proofs and fewer like \name{EProver} or \Metis 
replied the proof in an admissible file format.

@@

Previous studies have reported proof-reconstruction using proof assistants for classical logic where the development is at a mature stage.
In contrast, we choose a proof assistant for type theory
where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism. Then, the proof-reconstruction generates such proof-terms by reconstructing the proof replied by the \ATP.
However, some limitations arises by using type theory as we describe in Section~\ref{sec:limitations-type-theory}.

>>>>

\section{Introduction}
\label{sec:introduction}

Reconstructing and verifying proofs delivered by automatic theorem provers
(henceforth ATP) are non-trivial tasks.
In the last decades, \ATPs is fast becoming a key instrument in 
different disciplines (\eg~verifying cryptographic protocols for information security) and researchers have shown an increased interest to prove the validity of their deduction algorithms.
One reason to say that is the bugs found in many ATPs~\cite{Keller2013,Bohme2011,Fleury2014}.
For that reason, in order to give confidence to the user of these systems,
many ATPs has started to include in their outputs, the proof of their
conclusions. However, existing research recognizes that in many cases these proofs encode non-trivial reasoning
hard to reconstruct and therefore hard to verify. The proof-reconstruction
address this problem and becomes in some cases a reverse engineering of the
prover reasoning.

Therefore, the proof replied by the prover and its quality play an important role for proof-reconstruction. To verify such a proof, it is necessary to have
it in a consistent format, that is, a full script 
describing step-by-step with exhaustive details and without ambiguities, the derivation to get the proof.
For classical propositional logic (henceforth \CPL) from a list of at least forty\footnote{\ATPs 
available from the web
service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
provers were able to deliver proofs and fewer like \name{EProver} or \Metis 
replied the proof in an admissible file format.

@@

Previous studies have reported proof-reconstruction using proof assistants for classical logic where the development is at a mature stage.
Even though we choose a proof assistant for type theory
where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism. Then, the proof-reconstruction generates such proof-terms by reconstructing the proof replied by the \ATP.
However, some limitations arises by using type theory as we describe in Section~\ref{sec:limitations-type-theory}.
